Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-25 LatexNotes/Notes.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TKDV
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The truncated KdV equations}

@@

\subsubsection{My own reformulation}

@@

Then in dimensionless variables (after dropping the tildes), the system is given by
\begin{equation}
\eta_t + \frac{3}{2}\eps \eta \eta_{\xi} + \frac{2 \pi^2}{3} \delta^2 \eta_{\xi \xi \xi} = 0
\end{equation}
where we have the dimensionless variables
\begin{align}
\eps = a/h_0 , \quad \delta = h_0/\lambda_p
\end{align}
In these dimensionless variables, we have that $\eta$ is periodic for $x \in [0, 2\pi)$ and we have $\mean{\eta^2} = 1$, just as intended.
Note, in the experiments, $\delta = 0.33$ and $\eps$ lies in the range $2.4 \times 10^{-3}$ to $2.4 \times 10^{-2}$.

@@

The main difficulty I have with this formulation is that there is no reason to expect the spatial period of $u$ to have anything to do with the tank width $L_0$. More logically, the spatial period of $u$ should correspond to a characteristic wavelength in the problem, either the peak or maximum wavelength. The latter is more likely to be true in a literal sense, but I believe the peak wavelength provides a more reasonable scale for non-dimensionalization.

\subsection{Hamiltonian structure}
We will be using the truncated KdV equations (TKDV) with variable depth, in particular an abrupt depth change (ADC). The upstream depth is normalized to $1$ and the downstream (dimensionless) depth is $D_0$. Accordingly, the upstream and downstream Hamiltonians are given by
\begin{align}
\label{Hamiltonian}
& H^- = E_0^{1/2} H_3 - H_2 \\
& H^+ = D_0^{-13/4} E_0^{1/2} H_3 - D_0^{3/2} H_2 \\
\end{align}

>>>>

\np
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TKDV
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The truncated KdV equations}

@@

\subsubsection{My reformulation}

@@

Then in dimensionless variables (after dropping the tildes), the system is given by
\begin{equation}
\eta_t + \frac{3}{2}\eps \eta \eta_{\xi} + \frac{2 \pi^2}{3} \delta^2 \eta_{\xi \xi \xi} = 0
\end{equation}
where we have the dimensionless variables
\begin{align}
\eps = a/h_0 , \quad \delta = h_0/\lambda_p
\end{align}
In these dimensionless variables, we have that $\eta$ is periodic for $x \in [0, 2\pi)$ and we have $\mean{\eta^2} = 1$, just as intended.
Note, in the experiments, $\delta = 0.33$ and $\eps$ lies in the range $2.4 \times 10^{-3}$--$2.4 \times 10^{-2}$.

@@

The main difficulty I have with this formulation is that there is no reason to expect the spatial period of $u$ to be related to the tank width $L_0$. More logically, the spatial period of $u$ should correspond to a characteristic wavelength in the problem, either the peak or maximum wavelength. The latter is more likely to be true in a literal sense, but I believe the peak wavelength provides a more reasonable scale for non-dimensionalization.

Otherwise, the two formulations are completely equivalent. Notice that $\mu \lambda^{-3}$ in Andy's notation plays the role of $\delta^2$ in my notation, and $E_0^{1/2} \lambda^{-3/2}$ in Andy's notation plays the role of $\eps$ in my notation.

\np
\subsection{Hamiltonian structure}
We will be using the truncated KdV equations (TKDV) with variable depth, in particular an abrupt depth change (ADC). The upstream depth is normalized to $1$ and the downstream (dimensionless) depth is $D_0$. Accordingly, the upstream and downstream Hamiltonians are given by
\begin{align}
\label{Hamiltonian}
& H^- = E_0^{1/2} H_3 - H_2 \\
& H^+ = D_0^{-13/4} E_0^{1/2} H_3 - D_0^{3/2} H_2 \\
\end{align}
